14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-29 rules/rules19.tex
Rules: more in system descriptions
first draft competition wide recognition

\header{System description.}
%
As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
short (1-2 pages) description of the system, which \textbf{must} explicitly
acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or
\emph{derived} tool (see above).
In case of a \emph{wrapper} tool, it \textbf{must} also explicitly state
the exact version of each wrapped solver.
It \emph{should} further include
\begin{itemize}[itemsep=0ex]
  \item a list of all authors of the system and their present institutional
    affiliations,
  \item the basic SMT solving approach employed,
  \item details of any non-standard algorithmic techniques as well as
    references to relevant literature (by the authors or others),
  \item in case of a \emph{wrapper} or \emph{derived tool}: details of
    technical innovations by which a wrapper or derived tool expects to improve
    on the wrapped solvers or base solver
  \item appropriate acknowledgement of tools other than SMT solvers called by
    the system (e.g., SAT solvers) that are not written by the authors of the
    submitted solver, and
  \item a link to a website for the submitted tool.
\end{itemize}
System descriptions \textbf{must} be submitted \textbf{until the final solver
deadline}, and will be made publicly available on the competition website.

@@

\header{Division}
Within each track there are multiple divisions, and each division selects
benchmarks from a specific SMT-LIB logic in the SMT-LIB benchmark library.

@@

\subsubsection{Parallel Division Score}

@@

\subsubsection{Sequential Division Score}

@@

{\color{red} Details to be announced.}

>>>>

\header{System description.}
%
As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
short (1-2 pages) description of the system, which \textbf{must} explicitly
acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or
\emph{derived} tool (see above).
In case of a \emph{wrapper} tool, it \textbf{must} also explicitly state
the exact version of each wrapped solver.
A system description \emph{should} further include the following information
(unless there is a good reason otherwise):
\begin{itemize}[itemsep=0ex]
  \item a list of all authors of the system and their present institutional
    affiliations,
  \item the basic SMT solving approach employed,
  \item details of any non-standard algorithmic techniques as well as
    references to relevant literature (by the authors or others),
  \item in case of a \emph{wrapper} or \emph{derived tool}: details of
    technical innovations by which a wrapper or derived tool expects to improve
    on the wrapped solvers or base solver
  \item appropriate acknowledgement of tools other than SMT solvers called by
    the system (e.g., SAT solvers) that are not written by the authors of the
    submitted solver, and
  \item a link to a website for the submitted tool.
\end{itemize}
System descriptions \textbf{must} be submitted \textbf{until the final solver
deadline}, and will be made publicly available on the competition website.
Organizers will check that they contain sufficient information
and may withdraw a system if its description is not sufficiently updated upon
request

@@

\header{Divisions.}
Within each track there are multiple divisions, and each division selects
benchmarks from a specific SMT-LIB logic in the SMT-LIB benchmark library.

@@

\subsubsection{Parallel Score}

@@

\subsubsection{Sequential Score}

@@

In 2014 the SMT competition introduced a competition-wide scoring to allow it to award medals in the FLoC Olympic Games and has been awarded each year since. This scoring purposefully emphasized the breadth of solver participation by summing up a score for each (competitive) division a solver competed in. Whilst this rationale is reasonable, we observed that this score had become dictated by the number of divisions being entered by a solver.

This year we will replace the competition-wide score with two new \emph{rankings} that select one solver per division and then rank those solvers. The rationale here is to take the focus away from the number of divisions entered and focus on measures that make sense to use to compare different divisions.

\subsubsection{Biggest Lead Ranking}

This ranking aims to select the solver that \emph{won by the most} in some competitive division. The winners of each division are ranked by the distance between them and the next competitive solver in that division.

Let $\mathit{solved}(D,i)$ be the number of problems solved by the $i$th solver in division $D$. The rank of division $D$ is given as
\[
\frac{\mathit{solved}(D,1)+1}{\mathit{solved}(D,2)+1}
\]
The biggest lead winner is the winner of the division with the highest (largest) rank. This can be computed per scoring system e.g. separately for the sat and unsat score.

\subsubsection{Largest Contribution Ranking}

This ranking aims to select the solver that \emph{uniquely contributed} the most in some division, or to put another way, the solver that would be most missed. This is achieved by computing a solvers contribution to the \emph{virtual best solver} for a division.

The virtual best solver score for a division $D$ containing solvers $S$ is given as 
\[
\mathit{vbss}(D,S) = \sum_{b \in D} {\sf min}\{ \mathit{solvedIn}(s,b) \mid s \in S ~\mathit{and}~\mathit{solved}(s,b) \}
\]
where $\mathit{solved}(s,b)$ is true if solver $s$ solves benchmark $b$ and $\mathit{solvedIn}(s,b)$ is the amount of time solver $s$ takes to solve benchmark $b$. E.g. $\mathit{vbss}(D,S)$ is the smallest amount of time taken to solve all benchmarks solved in division $D$ using solvers in $S$.

Let $S$ be the set of competitive solvers competing in division $D$. The rank of solver $s \in S$ in division $D$ is then
\[
1- \frac{\mathit{vbss}(D,S-s) }{ \mathit{vbss}(D,S)}
\]
e.g. the difference in virtual best solver score when removing $s$ from the computation. This will be a number between 0 and 1 with 0 indicating that $s$ made no impact on the \emph{vbss} and 1 indicating that $s$ is the only solver that solved anything in the division.

The largest contribution winner is the solver across all divisions with the highest (largest) rank. Again, this can be computed per scoring system.
